Mobility Boomerang Plots

### 2021-09-01 notebooks/embedding_boomerang_plots.rmd
update notebooks

df <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_w2vfactors.csv") %>%
  select(cwts_org_no, l2norm) %>%
  left_join(meta, by = "cwts_org_no")

@@

sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/raw/2008-2019_inst_sizes.txt", delim = "\t") %>%
  group_by(cwts_org_no) %>%
  summarize(
    size = mean(person_count)
  )

@@

plot <- plotdata %>%
  ggplot(aes(x = size, y = l2norm, color = rank, shape = is.na(rank), label = full_name)) +
  geom_point() +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_continuous(
    limits = c(0, 7),
    breaks = c(2, 4, 6)
  ) +
  viridis::scale_color_viridis(
    name = "Times Rank", 
    option = "C",
    breaks = c(1, 50, 100)
  ) +
  scale_shape_manual(values = c(16, 1)) +
  #ggrepel::geom_label_repel(
  #  data = plotlabs,
  #  aes(label = label),
  #  color = "black",
  #  force = 50,
  #  min.segment.length = 0.1,
  #  alpha = 0.9,
  #  size = 3.5
  #) +
  guides(shape = F,
         color = guide_colorbar(reverse = T)) +
  theme_minimal() +
  annotate(geom = "label", x = 1.5e4, y = 3.6, label = "Harvard", size = 3.5) +
  annotate(geom = "label", x = 1.6e3, y = 3.65, label = "Princeton", size = 3.5) +
  annotate(geom = "label", x = 8.5e3, y = 5.9, label = "Univ Tennessee\nKnoxville", size = 3.5) +
  annotate(geom = "label", x = 1.8e2, y = 1.55, label = "Univ Alaska\nFairbanks", size = 3.5) +
  annotate(geom = "label", x = 4e2, y = 6.2, label = "NY Medical College", size = 3.5) +
  annotate(geom = "label", x = 2e1, y = 4.6, label = "Univ Michigan\nFlint", size = 3.4) +
  annotate(geom = "label", x = 6.8e1, y = 2.48, label = "Barry University", size = 3.5) +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(face = "bold"),
    legend.position = c(0.11, 0.852),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(color="black", size = 0.3),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("# Researchers") +
  ylab("L2 Norm")

>>>>

df <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_gamma1.0_w2vfactors.csv") %>%
  select(cwts_org_no, l2norm) %>%
  left_join(meta, by = "cwts_org_no")

@@

sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/2008-2019_inst_sizes_all.txt", delim = "\t")

@@

plot <- plotdata %>%
  ggplot(aes(x = size, y = l2norm, color = rank, shape = is.na(rank), label = full_name)) +
  geom_point() +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_continuous(
    limits = c(0, 7),
    breaks = c(2, 4, 6)
  ) +
  viridis::scale_color_viridis(
    name = "Times Rank", 
    option = "C",
    breaks = c(1, 50, 100)
  ) +
  scale_shape_manual(values = c(16, 1)) +
  #ggrepel::geom_label_repel(
  #  data = plotlabs,
  #  aes(label = label),
  #  color = "black",
  #  force = 50,
  #  min.segment.length = 0.1,
  #  alpha = 0.9,
  #  size = 3.5
  #) +
  guides(shape = F,
         color = guide_colorbar(reverse = T)) +
  theme_minimal() +
  annotate(geom = "label", x = 1.6e4, y = 3.55, label = "Harvard", size = 3.5) +
  annotate(geom = "label", x = 1.6e3, y = 3.5, label = "Princeton", size = 3.5) +
  annotate(geom = "label", x = 8.5e3, y = 5.8, label = "Univ Tennessee\nKnoxville", size = 3.5) +
  annotate(geom = "label", x = 1.8e2, y = 1.55, label = "Univ Alaska\nFairbanks", size = 3.5) +
  annotate(geom = "label", x = 4e2, y = 6.0, label = "NY Medical College", size = 3.5) +
  annotate(geom = "label", x = 1.5e1, y = 4.6, label = "Univ Michigan\nFlint", size = 3.4) +
  annotate(geom = "label", x = 6.8e1, y = 2.48, label = "Barry University", size = 3.5) +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(face = "bold"),
    legend.position = c(0.11, 0.852),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(color="black", size = 0.3),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("# Researchers") +
  ylab("L2 Norm")
